Attributions for Poverty in Post-Socialist Countries

### 2014-03-03 article2013.Rmd
Mikon muutokset pedariin. Palaan toimistolla asiaan liitetaulukon yms. osalta

---
title: "Attributions for Poverty in Post-Socialist Countries"
author: [Markus Kainu & Mikko Niemelä]
affiliation: Finland
date: February 27, 2014
header-includes:
    - \usepackage{fancyhdr}
    - \pagestyle{fancy}
    - \fancyhead[CO,CE]{}
    - \fancyfoot[CO,CE]{}
    - \fancyfoot[LE,RO]{\thepage}
abstract: Utilising The Life in Transition Survey (LiTS) conducted in 2010, the purpose of the paper is to examine public perceptions of the causes of poverty in Europe and Western Asia with special emphasis on post-socialist countries. The study applies multilevel techniques in order to analyse the role of individual and country-level explanatory factors as determinants of poverty attributions. As country-level determinants, paper analyses the changes in country's economic performance during the period of global financial crises, income inequality and the state of democracy. As individual-level determinants, the paper tests to what extent risk factors related to financial hardship are associated with perceptions of the causes of poverty.
keywords: poverty
output:
  pdf_document:
    toc: true
    number_section: true
---

>>>>

---
title: "Attributions for Poverty in Post-Socialist Countries"
author: [Markus Kainu & Mikko Niemelä]
affiliation: Finland
date: March 3, 2014
header-includes:
    - \usepackage{fancyhdr}
    - \pagestyle{fancy}
    - \fancyhead[CO,CE]{}
    - \fancyfoot[CO,CE]{}
    - \fancyfoot[LE,RO]{\thepage}
abstract: Utilising The Life in Transition Survey (LiTS) conducted in 2010, the purpose of the paper is to examine public perceptions of the causes of poverty in Europe and Western Asia with special emphasis on post-socialist countries. The study applies multilevel techniques in order to analyse the role of individual and country-level explanatory factors as determinants of poverty attributions. As country-level determinants, paper analyses the changes in country's economic performance during the period of global financial crises, income inequality and the state of democracy. As individual-level determinants, the paper tests to what extent risk factors related to financial hardship are associated with perceptions of the causes of poverty.
keywords: poverty
output:
  pdf_document:
    toc: true
    number_section: true
---
